Investigating the applications and limits of single particle light scattering using limited detection schemes

### 2022-11-09 Manuscript.tex
Update Manuscript.tex

\begin{abstract}
Combing light scattering techniques with optical trapping set ups poses a significant engineering challenge. We propose a optical tweezer set up that will allow for light scattering measurements of a trapped micro particle. The set up is constrained by the limited space available to place optical fibres within range of the trapped entity. This paper discusses how light scattering data from a trapped dimer can be used to predict the orientation of the dimer within the trap. This method can be extended for determining characteristics that influence the light scattering pattern. We also discuss the how to determine best possible arrangement of optical fibres that will provide the greatest accuracy in our prediction. We hope to take this work further with real experimental data from our own light scattering measurements.

>>>>

\begin{abstract}
While optical trapping is a well understood method for force transduction and detection,characterisation of trapped entities poses a two-fold challenge - one experimental concerning the arrangement of light detectors and the other, theoretical involving solving of the inverse light scattering problem. Combining static light scattering techniques with optical trapping poses significant engineering challenges due to the space constraints in a conventional optical trapping setup. We propose here a plausible scenario of detecting scattered light from an optically trapped asymmetric microstructure using a novel, multi-angle, optical-fibre based detection scheme and demonstrate how a Bayesian inference based analysis of the data simulated to mimic light scattering detection signals in such scenarios maybe used for solving the inverse light scattering problem and help characterise trapped entitites. To this end, we discuss the application of our method to infer the instantaneous orientations of an asymmetric microsphere dimer being trapped. We argue that this method can be extended for determining any characteristics of the trapped microstructure that influence the light scattering pattern.
